A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
new figure on transitioning and lil rewording on bead count section

We first assign each marked node $v$ of the skeleton an initial bead count $B^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
We also filter unmarked regions where the bead count remains constant.
\todo{Explaining why would have to refer forward to section about interpolating beadings}
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
If the upper node has the same bead count we mark all bones and nodes $v$ in between, and set the bead count $B^*_{v_0} = B^*_v = B^*_{v_1}$.

\todo{TODO: figure of basic bead counts left, middle with transition mids, right with transition ends.}

>>>>

We first assign each marked node $v$ of the skeleton an initial bead count $B^*_v \leftarrow b(2R(v))$, but it is modified in order to prevent high frequency changes in bead count and it is changed in order to account for smooth transitions in bead count.
See \cref{beading_transitioning_filtering__bead_count}.

We also filter unmarked regions where the bead count remains constant.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}) until we hit another marked node $v_1$.
If the upper node has the same bead count we mark all bones and nodes $v$ in between, and set the bead count $B^*_{v_0} = B^*_v = B^*_{v_1}$.
\todo{Explaining why would have to refer forward to section about interpolating beadings}

\begin{figure*}
\centering
\setlength{\figwidth}{\textwidth}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__bead_count.pdf}
\caption{Initial bead counts}\label{beading_transitioning_filtering__bead_count}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_mids.pdf}
\caption{Transition anchors}\label{beading_transitioning_filtering__transition_mids}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__filtered.pdf}
\caption{Filtered anchors}\label{beading_transitioning_filtering__filtered}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transition_ends.pdf}
\caption{Transition ends}\label{beading_transitioning_filtering__transition_ends}
\end{subfigure}
\begin{subfigure}{0.19\figwidth}
\includegraphics[width=\columnwidth]{sources/method/beading_transitioning_filtering__transitions_applied.pdf}
\caption{Radial bones}\label{beading_transitioning_filtering__transitions_applied}
\end{subfigure}
\caption{
Applying bead counts and transitioning on a shape showing the difference between a simple skeleton (top) and a mirrored version with small perturbations in the outline (bottom).
Outline in black, medial axis edges in red, radial edges in grey.
First we initialize the bead counts (black) in the marked regions (blue).
We then extract the anchor locations (purple) of the transitions to a different bead count should be.
We then filter out regions of constant bead count.
We then calculate the end locations (magenta, pink) of the transitions and modify the bead count at nodes in between to fractional values.
Finally we introduce nodes at the ends and introduce radial edges (purple) as per the trapezoidation constraint.
Transitioning is robust against small pertuirbations in the outline shape.
}
\label{beading_transitioning_filtering}
\end{figure*}
